Online reprocessing simulation for thorium-fueled molten salt breeder reactor

### 2017-07-31 msbr_reproc.tex
grammar
spelling and stuff

In this work, only the Zone I unit cell, where the fuel salt volume fraction is 
13.2\%, was considered. The neutron spectrum for Zone II cell, where the fuel 
salt volume fraction is 37\% is expected to be harder and the peak in thermal 
energy region is predicted to be much 
lower. To obtain a high-fidelity neutron energy spectrum, a full-core \gls{MSBR}
analysis is required.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
The depletion calculation of the \gls{MSBR} unit cell model for finding the 
equilibrium states was performed using the Serpent 2 Monte Carlo code to 
simulate simplified case of the online reprocessing and refueling to find 
equilibrium material composition. When running depletion calculation, the 
fission products are removed and fertile/fissile materials are added to fuel 
salt every 3 days. The important MSR feature, online reprocessing I\& refueling 
is implemented in the Serpent 2 material burnup routine. The results of this 
study indicate that from the depletion calculation the multiplication factor 
slowly decreases and reaches to the equilibrium state. The most obvious finding 
to emerge from the analysis of initial and equilibrium materials composition is 
that neutron energy spectrum is harder for equilibrium state because 
significant amount of heavy fission products were accumulated in the \gls{MSBR} 
core.

These results are contrary with those of Jeong and Park (2016) who suggested 
two different unit cell models and uses \gls{MCNP} with Python-script to 
simulate \gls{MSBR} online reprocessing to find equilibrium composition. This 
inconsistency may be due to different fuel fraction in the unit cell (Jeong and 
Park selected 20.6\% salt fraction). To obtain better results in online 
reprocessing simulation number of future efforts expected. First, depletion 
simulation will be performed using full-core tree-dimensional high-fidelity 
model of \gls{MSBR} developed in Serpent 2. In this case, different 
fuel-moderator volume ratios for the reactor Zone I, Zone II, annulus, 
reflectors would be taken into account to find accurate multiplication factor, 
neutron spectrum and, hence, depleted composition. Secondly, additional Serpent 
2 flow control system subroutine should be developed to simulate adjusting 
material flows (e.g. rate of removing $^{233}$Pa from the salt and adding 
fissile $^{233}$U from the tank for protactinium decay) depending upon current 
reactivity value which is more promising reactivity control method than moving 
control and safety rods. Finally, temperature effect of reactivity for both 
fuel salt and graphite should be calculated to find optimal effective 
multiplication factor range.

>>>>

In this work, only the Zone I unit cell, where the fuel salt volume fraction is 
13.2\%, was considered. The neutron spectrum for Zone II cell, where the fuel 
salt volume fraction is 37\% is expected to be harder and the peak in thermal 
energy region is predicted to be much 
lower. To obtain a high-fidelity neutron energy spectrum, a full-core \gls{MSBR}
analysis is required.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
The depletion calculation of the \gls{MSBR} unit cell model for finding the 
equilibrium states was performed using the Serpent 2 Monte Carlo code to 
simulate simplified case of the online reprocessing and refueling to find 
equilibrium material composition. When running depletion calculation, the 
fission products are removed and fertile/fissile materials are added to fuel 
salt every 3 days. The important MSR feature, online reprocessing \& refueling 
is implemented in the Serpent 2 material burnup routine. The results of this 
study indicate that from the depletion calculation the multiplication factor 
slowly decreases and reaches to the equilibrium state. The most obvious finding 
to emerge from the analysis of initial and equilibrium materials composition is 
that neutron energy spectrum is harder for equilibrium state because 
significant amount of heavy fission products were accumulated in the \gls{MSBR} 
core.

These results are contrary with those of Jeong and Park (2016) who suggested 
two different unit cell models and uses \gls{MCNP} with Python-script to 
simulate \gls{MSBR} online reprocessing to find equilibrium composition. This 
inconsistency may be due to different fuel fraction in the unit cell (Jeong and 
Park selected 20.6\% salt fraction). To obtain better results for this online 
reprocessing simulation, many future efforts are planned. First, a depletion 
simulation will be performed using a  full-core, three-dimensional, high-fidelity 
model of \gls{MSBR} developed in Serpent 2. In this case, different 
fuel-moderator volume ratios for the reactor Zone I, Zone II, annulus, 
reflectors would be taken into account to find accurate multiplication factor, 
neutron spectrum and, hence, depleted composition. Secondly, additional Serpent 
2 flow control system subroutine should be developed to simulate adjusting 
material flows (e.g. rate of removing $^{233}$Pa from the salt and adding 
fissile $^{233}$U from the tank for protactinium decay) depending upon current 
reactivity value which is more promising reactivity control method than moving 
control and safety rods. Finally, temperature effect of reactivity for both 
fuel salt and graphite should be calculated to find optimal effective 
multiplication factor range.
